---
title: "Got"
author: "Nicoline Jacob, Rebecca"
date: "2024-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)
library(here)
library(pdftools)
library(tidytext)
library(textdata) 
library(ggwordcloud)
```

```{r get-document}
got_path <- here("data","got.pdf")
got_text <- pdf_text(got_path)
```

```{r single-page}
got_p37 <- got_text[37]
got_p37
```
```{r split-lines}
got_df <- data.frame(got_text) %>% 
  mutate(text_full = str_split(got_text, pattern = '\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full)) 

```




```{r tokenize}
got_tokens <- got_df %>% 
  unnest_tokens(word, text_full)
got_tokens
```
```{r count-words}
got_wc <- got_tokens %>% 
  count(word) %>% 
  arrange(-n)
got_wc
```

```{r stopwords}
got_stop <- got_tokens %>% 
  anti_join(stop_words) %>% 
  select(-got_text)
View(stop_words)
```
```{r count-words2}
got_swc <- got_stop %>% 
  count(word) %>% 
  arrange(-n)
```


```{r skip-numbers}
got_no_numeric <- got_stop %>% 
  filter(is.na(as.numeric(word)))
```


```{r wordcloud-prep}

length(unique(got_no_numeric$word))
got_top100 <- got_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)

```

```{r wordcloud}
got_cloud <- ggplot(data = got_top100, aes(label = word)) +
  geom_text_wordcloud() +
  theme_minimal()

got_cloud
```

```{r wordcloud-pro}
ggplot(data = got_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n), shape = "star") +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colors = c("darkgreen","blue","red")) +
  theme_minimal()
```
```{r afinn}
get_sentiments(lexicon = "afinn")
afinn_pos <- get_sentiments("afinn") %>% 
  filter(value %in% c(3,4,5))
afinn_pos
```
```{r bing}
get_sentiments(lexicon = "bing")
```

```{r nrc}
get_sentiments(lexicon = "nrc")
```

```{r bind-afinn}
got_afinn <- got_stop %>% 
  inner_join(get_sentiments("afinn"))
```

```{r count-afinn}
got_afinn_hist <- got_afinn %>% 
  count(value)

# Plot them: 
ggplot(data = got_afinn_hist, aes(x = value, y = n)) +
  geom_col()
```

```{r afinn-2}
# What are these '2' words?
got_afinn2 <- got_afinn %>% 
  filter(value == 3)
```


```{r afinn-2-more}

unique(got_afinn2$word)

got_afinn2_n <- got_afinn2 %>% 
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(factor(word), n))

ggplot(data = got_afinn2_n, aes(x = word, y = n)) +
  geom_col() +
  coord_flip()

```
```{r summarize-afinn}
got_summary <- got_afinn %>% 
  summarize(
    mean_score = mean(value),
    median_score = median(value)
  )
```

```{r bind-bing}
got_nrc <- got_stop %>% 
  inner_join(get_sentiments("nrc"))
```


```{r check-exclusions}
got_exclude <- got_stop %>% 
  anti_join(get_sentiments("nrc"))
got_exclude_n <- got_exclude %>% 
  count(word, sort = TRUE)

head(got_exclude_n)
```

```{r count-bing}
got_nrc_n <- got_nrc %>% 
  count(sentiment, sort = TRUE)

ggplot(data = got_nrc_n, aes(x = sentiment, y = n)) +
  geom_col()
```

```{r count-nrc}
got_nrc_n5 <- got_nrc %>% 
  count(word,sentiment, sort = TRUE) %>% 
  group_by(sentiment) %>% 
  top_n(5) %>% 
  ungroup()

got_nrc_gg <- ggplot(data = got_nrc_n5, aes(x = reorder(word,n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, ncol = 2, scales = "free") +
  coord_flip() +
  theme_minimal() +
  labs(x = "Word", y = "count")
got_nrc_gg

ggsave(plot = got_nrc_gg, 
       here("figures","ipcc_nrc_sentiment.png"), 
       height = 8, 
       width = 5)

```

```{r nrc-lord}
lord <- get_sentiments(lexicon = "nrc") %>% 
  filter(word == "lord")
lord
```

**What are the most common meaningful words and what emotions do you expect will dominate this volume?**
#we exspect that there will be most negatives emotiones to this volume. 
#the line 174 shiws that both negative and positive words are most common 
#we found the most meaningfull words in line 144 to be "love", "loved", "grand","beautiful" and so on. 
**Are there any terms that are similarly ambiguous to the 'confidence' above?** 
#lord is a ambigious word, because it has  both positive and negative sentiments













